Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-06 minimax.tex
Random not parameterized
Table/Plot Comparison with Random pi=0.5

\subsection{Our previous presentation}
\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rd.\tiny{$\pi=0.1$}} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 8.07 & 0.52 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
			40 & 5.26 & 0.88 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
			60 & 2.37 & 0.93 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
			80 & 0.33 & 0.49 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
			100 & 0.0 & 0.02 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\caption{Average minimax regret in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
	\label{tab:comparison}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average regret after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

@@

The results are displayed in \cref{tab:comparison,fig:1020,fig:p}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 &  &  &  &  \\
			50 &  &  &  &  \\
			100 &  &  &  &  \\
			150 &  &  & &  \\
			200 &   &  &  &  \\
			250 &  & &  &  \\
			300 &&&& \\
			350 &&&& \\
			400 &&&& \\
			450 &&&& \\
			500 &&&& \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{fig:p}
\end{table}

>>>>

\subsection{Our previous presentation}
\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.06 & 0.49 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
			40 & 7.35 & 0.82 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
			60 & 5.74 & 1.03 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
			80 & 4.10 & 1.15 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
	\label{tab:comparison}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average MMR after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{MMR}$} & {$m\cdot n +m^?$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  \\
			5 & 15 & 1.5 & 80 &  \\
			5 & 20 & 2.0 & 110 &  \\
			10 & 20 & 2.0 & 340 &  \\
			10 & 30 & 3.0 & 527 &  \\
			15 & 30 & 3.0 &  &  \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{}
	\label{tab:linearity}
\end{table}

@@

The results are displayed in \cref{tab:comparison,fig:linearity,tab:twoP}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 &  &  &  &  \\
			50 &  &  &  &  \\
			100 &  &  &  &  \\
			150 &  &  & &  \\
			200 &   &  &  &  \\
			250 &  & &  &  \\
			300 &&&& \\
			350 &&&& \\
			400 &&&& \\
			450 &&&& \\
			500 &&&& \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{tab:twoP}
\end{table}
